---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ConformationalModel

<!-- badges: start -->
<!-- badges: end -->

The goal of ConformationalModel is to build kinetic models of ion channel receptors based on the interactions of conformational domains. 




## Installation

You can install the development version of ConformationalModel from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lmoffatt/ConformationalModel")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ConformationalModel)
```

lets define the conformational changes and its organization in domains

```{r}
changes <- conformationalChanges(
  conformational_changes = c("Binding", "Rocking"),
  agonists = c("ATP", "")
)

domains <- conformationaldomains(c(1, 2, 1, 2, 1, 2))

```



now define the interactions using the conformational changes ids and the domain ids: 

```{r}



interactions <- conformationalInteractions(
  labels = c("RB", "BR", "RBR"),
  players_ids = list(c(2, 1), c(1, 2), c(2, 1, 2)),
  domains_ids =
    list(list(c(6, 1), c(2, 3), c(4, 5)), list(c(1, 2), c(3, 4), c(5, 6)), list(c(6, 1, 2), c(2, 3, 4), c(4, 5, 6)))
)

```



we define the conductance interactions in the same way and the function that translate the conductance interactions to a defined interaction: 
```{r}

conductances <- conductanceInteractions(
  labels = c("Rocking_Current_factor"),
  players_ids = list(c(2)),
  domains_ids = list(list(c(2), c(4), c(6)))
)

conductance_info <- conductanceInteractionInfo(
  id_conductance_interaction = 1,
  kind = "equilibrium",
  leakeage_label = "Leakeage_current_ratio"
)

```


finally we define the standard states for some  conformational changes in terms of interactions of those standard states
```{r}

standard_states <- standardStates(
  id_conformational_change = c(2, 2, 2, 2),
  id_interaction = c(1, 2, 3, 3) ,
  pos_within_interaction = c(1, 2, 1, 3) ,
  count = c(1, 1, 1, 1)
)

```




with all this information we define a conformational model: 


```{r}
model = ConformationalModel(changes,
                            domains,
                            interactions,
                            conductances,
                            standard_states,
                            conductance_info)

```



now we define each one of the model parameters and we calculate the rates for those parameters
```{r}
parameters = c(
  Binding_on = 10.0,
  Binding_off = 10000,
  Rocking_on = 10000,
  Rocking_off = 100,
  RB = 10,
  RB_0 = 1,
  RB_1 = 1,
  BR = 10,
  BR_0 = 1,
  BR_1 = 1,
  RBR = 1,
  RBR_0 = 1,
  RBR_1 = 1,
  RBR_2 = 1,
  Rocking_Current_factor = 10,
  Leakeage_current_ratio = 1e-6
)


m = make_model(model, parameters)
m
```
