---
title: "scheme_11"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{scheme_11}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ConformationalModel)

```



lets define the conformational changes and its organization in domains

```{r}

changes <- conformationalChanges(
  conformational_changes = c("Binding", "Rocking"),
  agonists = c("ATP", "")
)


domains <- conformationaldomains(c(1, 2, 1, 2, 1, 2))

```



now define the interactions using the conformational changes ids and the domain ids: 

```{r}
interactions <- conformationalInteractions(
  labels = c("RB", "BR", "RBR"),
  players_ids = list(c(2, 1), c(1, 2), c(2, 1, 2)),
  domains_ids = list(list(c(6, 1), c(2, 3), c(4, 5)), list(c(1, 2), c(3, 4), c(5, 6)), list(c(6, 1, 2), c(2, 3, 4), c(4, 5, 6)))
)

```



we define the conductance interactions in the same way and the function that translate the conductance interactions to a defined interaction: 
```{r}

conductances <- conductanceInteractions(
  labels = c("Rocking_Current_factor"),
  players_ids = list(c(2)),
  domains_ids = list(list(c(2),c(4),c(6)))
)

conductance_info<-conductanceInteractionInfo(id_conductance_interaction = 1,kind = "equilibrium", leakeage_label = "Leakeage_current_ratio")

```


finally we define the standard states for some  conformational changes in terms of interactions of those standard states
```{r}

standard_states <- standardStates(id_conformational_change = c(2,2,2,2),id_interaction = c(1,2,3,3) ,pos_within_interaction = c(1,2,1,3) ,count =c(1,1,1,1) )

```




with all this information we define a conformational model: 


```{r}
model=ConformationalModel(changes,domains, interactions,conductances,
                                standard_states,
                                conductance_info)

```



now we define each one of the model parameters and we calculate the rates for those parameters
```{r}
parameters=c(Binding_on=10.0,Binding_off=10000,Rocking_on=10000,Rocking_off=100,RB=10, RB_0 =1,RB_1= 1, BR=10, BR_0=1, BR_1=1,RBR= 1, RBR_0=1, RBR_1=1, RBR_2=1, Rocking_Current_factor=10, Leakeage_current_ratio=1e-6)


m = make_model(model, parameters)
m
```




```{r}

n_states=g_ConformationalStates_data(model,1:24)
g_ConformationalStates(n_states)
```


```{r}
g_States_and_Rates(model, m$Q0, m$Qa, 1:24)
```

